Optimal management of a stochastically varying population when policy adjustment is costly

### 2014-06-05 manuscripts/manuscript.Rmd
no need to keep tex
use facet_wrap for better scaling

output:
  pdf_document:
    keep_tex: true
    template: components/elsarticle.latex
    fig_caption: true
---

@@

with_xcor_plot <- 
ggplot(figure4_df, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
  facet_wrap(~variable, scales = "free_y") +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line")
with_xcor_plot

ggplot(subset(figure4_df, statistic != "cross.correlation"), 
       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  facet_grid(statistic ~ timeseries, scale="free_y")

>>>>

output:
  pdf_document:
    template: components/elsarticle.latex
    fig_caption: true
---

@@

with_xcor_plot <- 
ggplot(figure4_df, aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn)) + 
  facet_wrap(~variable, scales = "free_y") +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line")
with_xcor_plot
```

```{r Figure_4_alt, fig.cap="Variance and autocorrelation of stock dynamics and harvest dynamics, as a function of the penalty coefficient.  Adjustment penalty is calculated as percentage of the maximum expected NPV in the basic case with no policy adjustment costs.", fig.height=8, fig.width=8}
ggplot(subset(figure4_df, statistic != "cross.correlation"), 
       aes(penalty_fraction, value, fill=penalty_fn, col=penalty_fn))  +
  stat_summary(fun.y = mean, 
               fun.ymin = function(x) mean(x) - sd(x), 
               fun.ymax = function(x) mean(x) + sd(x), 
               geom = "ribbon", alpha=0.3, colour=NA) +
  stat_summary(fun.y = mean, geom = "line") + 
  facet_wrap(~ timeseries + statistic, scale="free_y")
